Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-08-06 manuscript/manuscript.Rmd
Adding new word counts
Fixing attributions and moving running head down

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author:
  - William Kumler,$^a$ Wei Qin,$^{a*}$ Rachel A. Lundeen,$^a$ Benedetto Barone,$^b$ Laura T. Carlson,$^a$ Anitra E. Ingalls$^a$#
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: limnology-and-oceanography.csl
---

$^a$School of Oceanography, University of Washington, Seattle, WA, USA

$^b$Daniel K. Inouye Center for Microbial Oceanography: Research and Education and Department of Oceanography, University of Hawai'i at Mānoa, Honolulu, HI, USA

@@

\#Address correspondence to Anitra E. Ingalls, aingalls\@uw.edu

\*Present Address: School of Biological Sciences, Institute for Environmental Genomics, University of Oklahoma, Norman, OK, USA

  - Abstract: 216
  - Importance: 123
  - Main text (excluding Methods, figure captions, references, etc.): 5453

>>>>

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author:
  - William Kumler,$^1$ Wei Qin,$^{1+}$ Rachel A. Lundeen,$^1$ Benedetto Barone,$^2$ Laura T. Carlson,$^1$ Anitra E. Ingalls$^{1*}$
output: 
  word_document:
    reference_docx: Frontiers_Template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: frontiers-in-marine-science.csl
---

$^1$School of Oceanography, University of Washington, Seattle, WA, USA

$^2$Daniel K. Inouye Center for Microbial Oceanography: Research and Education and Department of Oceanography, University of Hawai'i at Mānoa, Honolulu, HI, USA

$^*$Correspondence: Anitra E. Ingalls, aingalls\@uw.edu

$^+$Present Address: School of Biological Sciences, Institute for Environmental Genomics, University of Oklahoma, Norman, OK, USA

  - Main text (excludes the abstract, section titles, figure and table captions, funding statement, acknowledgments, and references): 7,236
  - Number of figures: 6
  - Number of tables: 0

@@
